Reproductive Allocation Calculations

### 2015-03-24 leaflifespan.Rmd
Load all data files via remake

# InvestmentSummary <- InvestmentSummary
# names(InvestmentSummary)[1] <- "individual"

LMA <- read.csv("data/LMA_short.csv",header=TRUE,stringsAsFactors=FALSE)%>%
  filter(species!="" & species!=" ")

wood <- read.csv("data/woodDensity.csv", header=TRUE,stringsAsFactors=FALSE)%>%
  filter(use=="use")

seedsize <- read.csv("data/seedsize.csv", header=TRUE,stringsAsFactors=FALSE)

# leaf lifespan data
raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,stringsAsFactors=FALSE) %>%
  filter(dont_use!="dead" & dont_use!="dont_use")

# Create new dataset taking only count measures, bc these are ultimately what we want
leaf_lifespan <- raw_leaf_lifespan %>%
  select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

@@

# get average leaves per length for spp
leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, stringsAsFactors=FALSE) %>%
  filter(use=="yes") %>%
  mutate(count_per_length = leaf_count/length_mm) %>%
  group_by(species) %>%
  summarise(count_per_length = mean(count_per_length, na.rm=TRUE))

>>>>

LMA <- filter(LMA_raw, species!="" & species!=" ")

wood <- filter(woodDensity_raw, use=="use")

seedsize <- seedSize_raw

# leaf lifespan data
leaf_lifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
              select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

@@

# get average leaves per length for spp
leaves_per_length_spp <-  filter(leavesPerLength_raw,use=="yes") %>%
  mutate(count_per_length = leaf_count/length_mm) %>%
  group_by(species) %>%
  summarise(count_per_length = mean(count_per_length, na.rm=TRUE))
